My title

### 2022-04-11 outputs/paper/paper.Rmd
update on file structure

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - Charles Lu
  - Mahak Jain
  - Yujun Jiao
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "Using data extracted from Kenya’s Demographic and Health Surveys in 1998, this analysis aims to study the Kenyans’ perception of their risk of getting AIDS. By analyzing the age, number of sex partners, province, and education of the survey’s participants, results show that these factors all have different levels of impact on people’s risk of being infected. R [@citeR] is used in this report to create visualizations for the results. In the future, this report can help scholars to dive deeper into the history of the sexually-transmissible disease, study the correlation between the transmission rate and social backgrounds, and aid the authorities in making governmental or health-related plans. "
header-includes:
  - \usepackage{placeins}
output:
  bookdown::pdf_document2:
    latex_engine: xelatex
    toc: true
    fig_caption: yes
bibliography: references.bib
thanks: "https://github.com/R300G/paper4_placeholder_name"
---

>>>>

---
title: "My title"
author: 
  - Charles Lu
  - Mahak Jain
  - Yujun Jiao
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "Using data extracted from Kenya’s Demographic and Health Surveys in 1998, this analysis aims to study the Kenyans’ perception of their risk of getting AIDS. By analyzing the age, number of sex partners, province, and education of the survey’s participants, results show that these factors all have different levels of impact on people’s risk of being infected. R [@citeR] is used in this report to create visualizations for the results. In the future, this report can help scholars to dive deeper into the history of the sexually-transmissible disease, study the correlation between the transmission rate and social backgrounds, and aid the authorities in making governmental or health-related plans. "
header-includes:
  - \usepackage{placeins}
output:
  bookdown::pdf_document2:
    latex_engine: xelatex
    toc: true
    fig_caption: yes
bibliography: references.bib
thanks: "https://github.com/R300G/paper4_placeholder_name"
---
